\vspace{-0.25em}\thetitle

### 2009-07-24 paper.tex
...

Our answer to the question of why low-dimensional linear structure appears in the feature-frequency representation of network traffic can be posed in the form of a model.
A mixture model, to be specific.

>>>>

Our answer to the question of why low-dimensional linear structure appears in the feature-frequency representation of network traffic can be posed in the form of a model.
A mixture model, to be specific.
We propose to view each flow as having a probability distribution of possible behaviors it could exhibit.
% We propose that the behavior of each flow is drawn from a probability distribution on a space possible behaviors.
We hypothesize that the behavior distribution for most flows is a mixture of a relatively small set of ``basic behaviors.''
Moreover, only even smaller subsets of these basic behaviors are ever mixed with each other.

% Mixture modeling expresses probability densities as convex combinations of constituent probability distributions:
% \begin{align}\eqn{mixture-model}
%   q_i(x) = \sum_{j=1}^r w_{ij} p_j(x),
% \end{align}
% Here $q_i$ and $p_j$ are density functions, and $w_{ij}$ are nonnegative weights, summing to unity for each $i$.
% \Equation{mixture-model} says that each of the distributions $q_i$ is a convex mixture of the
